### 2021-04-05 paper/ase21/abstract.tex
Updated abstract

  To alleviate this problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using
  \textit{bug checkers}.  For a given specification, our tool first compiles
  each abstract algorithm written in a structured natural language to the
  corresponding function of $\ires$, which is an untyped intermediate
  representation for ECMAScript.  Then, it performs type analysis for compiled
  functions with specification types defined in the given ECMAScript.  Based on
  the result of type analysis, $\tool$ detects specification bugs using four
  different bug checkers.  Moreover, to increase precision of type analysis, we
  also present \textit{refinement} for type analysis, which prunes out
  infeasible abstract states by using conditions in assertions and branches.
  We evaluated $\tool$ with all 787 different versions of ECMAScript existed in
  the official repository for the recent three years (from 20 March 2018 to 9
  March 2021).  Our tool detected \inred{XXX} specification bugs including only
  \inred{XXX} false alarms caused by the imprecision of type analysis.  Among
  \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
  \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
  version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX} newly
  found bugs and they are confirmed by the committee.
\end{abstract}

>>>>

  To alleviate this problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using
  \textit{bug checkers}.  For a given specification, our tool first compiles
  each abstract algorithm written in a structured natural language to the
  corresponding function of $\ires$, which is an untyped intermediate
  representation for ECMAScript.  Then, it performs type analysis for compiled
  functions with specification types defined in ECMAScript.  Based on the result
  of type analysis, $\tool$ detects specification bugs using four different bug
  checkers.  Moreover, to increase precision of type analysis, we also present
  \textit{refinement for type analysis}, which prunes out infeasible abstract
  states by using conditions of assertions and branches.  We evaluated $\tool$
  with all \inred{787} different versions of ECMAScript existed in the official
  repository for the recent three years (\inred{from 20 March 2018 to 9 March
  2021}).  Our tool detected \inred{XXX} specification bugs including only
  \inred{XXX} false alarms caused by the imprecision of type analysis.  Among
  \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
  \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
  version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX} newly
  found bugs and they are confirmed by the committee.
\end{abstract}
